Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
lemma 3.1 stuff

\todo{Include one of the following, if the first one, include a 
remark for quotient}
\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
generated in degree 1, is equipped with a monomial ordering $\prec$.
 Let $\phi:k[x_1, \ldots, x_n] \rightarrow B$ be a map of graded
rings with kernel $I,$ such that $I$ is generated by elements $f_1,
\ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
is of the form $x_k$. Then, the elements $f_i$ determine minimal
generators for $I$.
\end{lem}
\begin{proof}
Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \rightarrow B
\]
\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
\todo{This ordering isn't quite right. 
We need to preserve the ordering on quadratic terms}
By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{rem}
In particular, in the case of
\[
	\begin{tikzcd}
		I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
		\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
		I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
inducing
\[
	I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
\]
\todo{how do we make this proof?}
\end{rem}

%
%\begin{lem}
%\label{lem:minimal_quadratic_2}
%Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
%generated in degree 1 that are equipped with monomial ordering $\prec$.
 %Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
%rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
%\[
	%\begin{tikzcd}
	%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	%\end{tikzcd}
%\]
%Further suppose that $I'$ is generated over $I$ by elements $f_1,
%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
%is of the form $y_i$. Then, the elements $f_i$ determine minimal
%generators for $I'$ over $I$.
%\end{lem}
%
%\begin{proof}
%Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
%degree 1. Then,
%\[
	%\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
%\]
%\[
	%\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
%\]
%
%
%\noindent
%determines map of rings, no longer necessarily graded. 
%By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Grobner basis,
%\[
	%\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
%\]
%so
%\[
	%\dim_k (I'/I)_2=j.
%\]
%This implies any set of
%generators for $I$ must have at least $j$ elements. Since $f_1,
%\ldots, f_j$ is such a set, it is minimal.
%\end{proof}
%
%
%\begin{rem}
%\label{rem:minimal_quadratic_trivial_case}
%It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
%case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
%are $k$-minimal generators for $I'$ (over the trivial base vector
%space). 
%\end{rem}

@@

\begin{proof}
By
our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
corresponds to the best lower approximation $\frac{c_j}{d_j}$. Recall from the previous 
paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l= 1$ and if 
$d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1. For 
convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$. In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
is not well-defined, just pick an arbitrary element of $R_{\halfcan'}$ for $z_l$ ensuring that the 
expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
is irrelevant, and only makes writing out cases more convenient. Therefore, we can write
\[
	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
\]

@@

\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number. What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$}
\begin{enumerate}
	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}$.
	\item[(Ad-ii)] Either $e_j' = 3$ for all $j \in \{1, \ldots, r\}$
		or any generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] The minimality condition
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

@@

We next show $y_{i, e_i}$ also satisfies the second part of the
claim of $(a),$ by considering separately the cases of whether $j
\in S(i, 0),$ and $j \notin S(i,0)$.

@@

To show (c), we wish to show that $f := y_{i, e_i}z \in R'$ for $z
\neq y_{i, e_i} \text{ or } y_{i, e_i'}$. Note that $f \in R$ lies
in $R'$ if and only if for all $j \in J$ we have
\begin{align*}
	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
\end{align*}

\noindent
We now check this in three cases, depending on whether $j \notin \{
i \} \cup S(i, 0), j = i,$ or $j \in S(i, 0)$.

@@

Finally, to check (e), we will first show that $(\sx,J)$ is
admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
strictly monotonic in the $e_i$ and hence also holds for $(\sx,J)$.
Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
definition. This is where we use that (Ad-iii) holds for $d > 0$
and not just for $d = 0$.

Finally, if $(\sx , J)$ is admissible then so is $(\sx, W)$ for any
$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
\end{proof}

@@

\begin{thm}
\label{thm:high_generators_relations}
Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

\begin{proof}
Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X + 2 K_X + \Delta$.
By Lemma ~\ref{lem:generation_5} and Proposition
~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta,
\halfcan_X)$. Next, consider a divisor of the form $\halfcan' =
\halfcan_X + \frac{1}{3} P_i$. Then, the theorem holds for $(\sx,
\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-two-induction-high-genus}
 if $P_i$ is a basepoint of $\halfcan'$ or by Lemma
~\ref{lem:deg1-sat-ind} if $P_i $ is not a basepoint of $L'$. Note,
in the case $P$  is a not basepoint of $\halfcan'$, Equation
~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d
\geq 3$.

In this case, we claim $(\sx',L',\{1\})$ is admissible. Indeed, (Ad-
i) holds by part (a) of Lemmas
~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind},
(Ad-ii) holds by part (b) of Lemmas
~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind},
and (Ad-iii) holds as $5\deg L \geq 5(g-1)> 2g-1.$ Therefore, by
Lemma ~\ref{lem:n-3s-admissible} , Any triple of the form $(\sx', L',
\{1,\ldots, r\})$ is admissible, with $e_1 = \cdots = e_r = 3$.
Hence, by Corollary ~\ref{cor:raise-stacky-order}, this theorem 
holds for all log spin curves $(\sx, L, J)$. 
\end{proof}

@@

\section{Further Research}
\label{sec:further-questions}
\begin{itemize}
	\item More on fractional modular forms
	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_11} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})? \todo{Possibly think more about this} 
	\item Generic Initial ideal (and other genericness properties?)
\end{itemize}

>>>>

\todo{Include one of the following, if the first one, include a 
remark for quotient}
\iffalse{
\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
generated in degree 1, is equipped with a monomial ordering $\prec$.
 Let $\phi:k[x_1, \ldots, x_n] \rightarrow B'$ be a map of graded
rings with kernel $I'$, such that $I'$ is generated by elements $f_1,
\ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
is of the form $x_k$. Then, the elements $f_i$ determine minimal
generators for $I$.
\end{lem}
\begin{proof}
Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \rightarrow B
\]
\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
\todo{This ordering isn't quite right. 
We need to preserve the ordering on quadratic terms}
By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{rem}
In particular, in the case of
\[
	\begin{tikzcd}
		I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
		\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
		I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
inducing
\[
	I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
\]
\todo{how do we make this proof?}
\end{rem}
}\fi

\begin{lem}
\label{lem:minimal_quadratic_2}
Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
generated in degree 1 that are equipped with monomial ordering $\prec$.
Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
\[
	\begin{tikzcd}
	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
Further suppose that $I'$ is generated over $I$ by elements $f_1,
\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
is of the form $y_i$. Then, the elements $f_i$ determine minimal
generators for $I'$ over $I$.
\end{lem}

\begin{proof}
Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
\]
\[
	\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
\]

\noindent
determines map of rings, no longer necessarily graded. 
By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Grobner basis,
\[
	\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
\]
so
\[
	\dim_k (I'/I)_2=j.
\]
This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{rem}
\label{rem:minimal_quadratic_trivial_case}
It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
are $k$-minimal generators for $I'$ (over the trivial base vector
space). 
\end{rem}

@@

Before presenting a proof of this, we first prove a lemma that will allow parts $(b)$ and $(c)$ to immediately follow from an appropriate construction of generators in part $(a)$.

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan$ and $\halfcan'$ are $\mathbf{Q}$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.  Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose $S$ is a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.  Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $R_{\halfcan'}$.  Moreover, suppose there is some ordering $\prec$ such that if $f\in S$ and $g\not\in S, g\not\in R_{\halfcan'}$ is a quadratic monomial in $x_1, \ldots, x_m, y_1, \ldots, y_n$ in the same degree as $f$, then $g\prec f$.  Then if $I$ and $I'$ are the ideal of relations of $R_{\halfcan'}$ and $R_{\halfcan}$ with the given generating sets, then 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
Furthermore, if $T$ consists only of quadratic monomials, then $I$ is minimally generated over $I'$ by a Grobner Basis with an initial term for each element of $T$.
\end{lem}
\begin{proof}

\end{proof}

\begin{proof}[Proof of Lemma \ref{lem:deg1-sat-ind}]
By
our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$.  Choose an element of the form $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ as described in the previous paragraph, in degree with $d_l= 1$ and if 
$d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1. For 
convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$. In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
is not well-defined, just pick an arbitrary element of $R_{\halfcan'}$ for $z_l$ ensuring that the 
expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
is irrelevant, and only makes writing out cases more convenient. Therefore, we can write
\[
	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
\]

@@

\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number. What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$}
\begin{enumerate}
	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}$.
	\item[(Ad-ii)] Any generator $z \neq y_{i, e_i'}$
		of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] The minimality condition
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

@@

We next show $y_{i, e_i}$ also satisfies the second part of the
claim of $(a),$ by considering separately the cases of whether $j
\in S(i,0),$ and $j \notin S(i,0)$.

@@

To show (c), we wish to show $y_{i, e_i}z \in R'$ for $z \neq y_{i, e_
i}, y_{i, e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
all $j \in J$ we have
\begin{align*}
	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
\end{align*}

\noindent
We now check this in three cases, depending on whether $j \notin \{
i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.

@@

Finally, to check (e), we will first show that $(\sx,J)$ is
admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
definition. This is where we use that (Ad-iii) holds for $d > 0$
and not just for $d = 0$.

Finally, if $(\sx , J)$ is admissible then so is $(\sx,W)$ for any
$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
\end{proof}

@@

\begin{thm}
\label{thm:general_generators_relations}
Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

\begin{proof}
Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X + 2 K_X + \Delta$. By Lemma ~\ref{lem:generation_5} and Proposition ~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta, \halfcan_X)$. Next, consider a divisor of the form $\halfcan' = \halfcan_X + \frac{1}{3}P_i$. Then, the theorem holds for $(\sx,\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-two-induction-high-genus} if $P_i$ is a basepoint of $\halfcan'$ or by Lemma ~\ref{deg1-sat-ind} if $P_i$ is not a basepoint of $L'$. Note, in the case $P$ is a not basepoint of $\halfcan'$, Equation ~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d \geq 3$.

In this case, we claim $(\sx',L',\{1\})$ is admissible. Indeed, (Ad-i) holds by part (a) of Lemmas ~\ref{lem:sat-two-induction-high-genus} and ~\ref{deg1-sat-ind}, (Ad-ii) holds by part (b) of Lemmas ~\ref{lem:sat-two-induction-high-genus} and ~\ref{deg1-sat-ind}, and (Ad-iii) holds as $5\deg L \geq 5(g-1)> 2g-1.$ Therefore, by Lemma ~\ref{lem:n-3s-admissible}, Any triple of the form $(\sx',L',\{1,\ldots, r\})$ is admissible, with $e_1 = \cdots = e_r = 3$. Hence, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for all log spin curves $(\sx, L, J).$ 
\end{proof}

@@

\section{Further Research}
\label{sec:further-questions}
\begin{itemize}
	\item More on fractional modular forms
	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_11} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})? \todo{Possibly think more about this} 
	\item Generic Initial ideal (and other genericness properties?)
	\item Complete minimal generation
\end{itemize}
